\ttitle

### 2013-07-03 Chapters/Chapter3.tex
Rough finish of chapter 2
chapter 3: svm outlier

% Chapter 3

\chapter{Experiments} % Main chapter title

\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter1}

\lhead{Chapter 3. \emph{Experiments}} % This is for the header on each 
%page - 
%perhaps a shortened title

%----------------------------------------------------------------------------------------

\section{}

>>>>

% !TEX root = ../main.tex
% Chapter 3

\chapter{Change detection by Support Vector Machines}

\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter3}

\lhead{Chapter 3. \emph{Change detection by Support Vector Machines}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
\section{Outline}
\emph{Not intented for the reader.}
\begin{itemize}
  \item Explain the connection between change detection and outlier detection
  \item Explain why and how SVM can be used for outlier detection, and thus for change detection in time series
  \item Explain options when using SVM, such as RBF kernel
  \item Relate characteristics of (accelerometer) data to the used (RBF?) kernel
  \item Define some quality metrics --> this should be in a different chapter (About experiments)
  \item Note: try to avoid the perspective of \emph{density estimation}. Instead: \emph{data description} or \emph{boundary description}.
\end{itemize}

\input{./Chapters/Chapter3/outlier_detection}
\input{./Chapters/Chapter3/one_class_svm}
\input{./Chapters/Chapter3/svm_parameters}
\input{./Chapters/Chapter3/data_characteristics}
\input{./Chapters/Chapter3/quality_metrics}
